Food Deserts in Chicago

### 2016-11-27 presentation.Rmd
Added count people in food desert

## Where are food deserts in Chicago

```{r, out.width = "600px", echo = FALSE}
knitr::include_graphics("deserts_plot.png")
```

>>>>

## Where are food deserts in Chicago
```{r, include = FALSE}
load('all_data')
```
```{r, out.width = "600px", echo = FALSE}
knitr::include_graphics("deserts_plot.png")
```

## Number of people living in a food desert
According to the data and methodology used, estimate `r sum(all_data[all_data$desert, 'TOTAL.POPULATION'], na.rm = TRUE)` people living in a food desert. This is similar, but not exactly the same as previous estimates. In fact, other studies give a higher estimate.
